Liveness-Based Garbage Collection for Lazy Languages

### 2015-11-28 paper/paper.tex
table and fig.

\newcommand{\hgt}{2.9cm}
\begin{figure*}[t]
\renewcommand{\arraystretch}{.1}
\begin{tabular}{@{}c@{}@{}c@{}}
%%    \hskip -4mm{\epsfig{file=lambda.eps, height=\hgt}}
%%    & {\epsfig{file=lambda_win.eps, height=\hgt}}
%% \\ \hskip -4mm{\epsfig{file=nperm.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=nperm_win.eps, height=\hgt}}
%% \\ \hskip -4mm{\epsfig{file=treejoin.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=treejoin_win.eps, height=\hgt}}
%% \\ \hskip -4mm{\epsfig{file=lcss.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=lcss_win.eps, height=\hgt}}
%% \\ \hskip -4mm{\epsfig{file=sudoku.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=sudoku_win.eps, height=\hgt}}
%% \\ \hskip -4mm{\epsfig{file=fibheap.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=fibheap_win.eps, height=\hgt}}
%% \\ \hskip -4mm{\epsfig{file=nqueens.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=nqueens_win.eps, height=\hgt}}
%% \\ \hskip -4mm{\epsfig{file=knightstour.eps, height=\hgt}}
%% &  \hskip -4mm{\epsfig{file=knightstour_win.eps, height=\hgt}}
   \hskip -4mm{\epsfig{file=lambda_win.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=nperm_win.eps, height=\hgt}}
\\   \hskip -4mm{\epsfig{file=treejoin_win.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=lcss_win.eps, height=\hgt}}
\\   \hskip -4mm{\epsfig{file=sudoku_win.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=fibheap_win.eps, height=\hgt}}
\\  \hskip -4mm{\epsfig{file=nqueens_win.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=knightstour_win.eps, height=\hgt}}
%\\ (a) & (b)
\end{tabular}%\vskip -10mm
 \caption{Memory usage.  
%% Column (a) shows complete  usage, column 
%%    (b) enlarges  a part  of the  usage.  
The blue and the red curves indicate the number of cons
cells  in  the  active   semi-space  for  RGC  and  LGC
respectively.  The black curve represents the number of
reachable cells and the  lightblue curve represents the
number  of  cells  that  are actually  live  (of  which
liveness analysis does a static approximation).  x-axis
is the time measured  in number of cons-cells allocated
(scaled down by factor $10^5$). y-axis is the number of
cons-cells (scaled down by $10^3$).}
\label{fig:memory-usage} \figrule
\end{figure*}

>>>>

\newcommand{\hgt}{2.9cm}
\begin{figure*}[t]
\renewcommand{\arraystretch}{.1}
\begin{tabular}{@{}c@{}@{}c@{}@{}c@{}}
   \hskip -4mm{\epsfig{file=fibheap_win.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=sudoku_win.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=nperm_win.eps, height=\hgt}}
\\ \hskip -4mm{\epsfig{file=paraffins_win.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=lcss_win.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=huffman_win.eps, height=\hgt}}
\\ \hskip -4mm{\epsfig{file=knightstour_win.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=nqueens_win.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=deriv_win.eps, height=\hgt}}
%\\ (a) & (b)
\end{tabular}%\vskip -10mm
 \caption{Memory usage.  
%% Column (a) shows complete  usage, column 
%%    (b) enlarges  a part  of the  usage.  
The blue and the red curves indicate the number of cons
cells  in  the  active   semi-space  for  RGC  and  LGC
respectively.  The black curve represents the number of
reachable cells and the  lightblue curve represents the
number  of  cells  that  are actually  live  (of  which
liveness analysis does a static approximation).  x-axis
is the time measured  in number of cons-cells allocated
(scaled down by factor $10^5$). y-axis is the number of
cons-cells (scaled down by $10^3$).}
\label{fig:memory-usage} \figrule
\end{figure*}
